LSOA domestic Electricty and Gas maps

### 2021-09-13 LSOA domestic Elec and Gas.Rmd

# or without colour but using facets for Local Authorities
solent_gasex <- filter(solent_gas,100*(dg_diff/mean_dg2010)<50)
ggplot(solent_gasex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/mean_dg2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change",
       caption = "Mean gas kWh 2010-2019, all Solent LSOAs with outlier removed") +
  facet_wrap(la_name ~ .)

>>>>

# or without colour but using facets for Local Authorities
solent_gasex <- filter(solent_gas,100*(dg_diff/mean_dg2010)<50)
ggplot(solent_gasex, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(dg_diff/mean_dg2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change in Gas consumption",
       caption = "Mean gas kWh 2010-2019, all Solent LSOAs with outlier removed") +
  facet_wrap(la_name ~ .)
